Towards Compiler-Agnostic Performance in Finite-Difference Codes. (TBC)

### 2014-11-20 shallow_perf.tex
WIP on the first paragraph

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HE" in caps to complete the first word.
\IEEEPARstart{T}{he} challenge presented to the developers of
scientific software by the drive towards Exascale computing is
considerable.

@@

We shall see that these optimisations do not always result in improved
performance. Whether or not they do so depends both on the compiler
and the problem size. We also emphasise that the aim of these
optimisations is to recover, as far as is possible, the structure of
the original version of the code. It may well be that transforming the
code into some other structure would result in better performance on a
particular architecture. However, exploring this optimisation space is
beyond the scope of the present work.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HE" in caps to complete the first word.
\IEEEPARstart{T}{he} challenge presented to the developers of
scientific software by the drive towards Exascale computing is
considerable. With power consumption becoming the overriding design
constraint, CPU clock speeds are falling and the complex,
multi-purpose compute core is being replaced multiple, simpler
cores. This philosophy can be seen at work in the rise of so-called
accelerator based machines in the Top 500 List~\cite{top500} of
supercomputers: five of the top-ten machines in the November 2014 list
make use of Intel Xeon Phi's or NVIDIA GPUs. Four of the remaining
five machines in the top ten are IBM BlueGene/Qs, the CPU of which has
hardware support for running 64 threads.

@@

We shall see that these transformations do not always result in improved
performance. Whether or not they do so depends both on the compiler
and the problem size. We also emphasise that the aim of these
optimisations is to recover, as far as is possible, the structure of
the original version of the code. It may well be that transforming the
code into some other structure would result in better performance on a
particular architecture. However, exploring this optimisation space is
beyond the scope of the present work.
